### 2018-04-16 Manuscripts/model-descriptions/packer/gamma_invariance.tex
New PACKER and CopyTweak implemented with gamma (tradeoff) as a multiplier for the contrast-category members only. Lets see how thje fits go! Still need to optimise the chtc code - there should be at least one more commit before sending this off to fit.
New fits seem good. CHTC code cleaned up. Still working on Hierarchical Bayes with representation?

%!TEX output_directory = latex_out/

@@

\section{The PACKER Model: Producing Alike or Contrasting Knowledge with Exemplar Representations}

@@

Where $f(x_j)$ is a function specifying each stored example's degree of contribution toward generation. Although $f(x_j)$ may be set arbitrarily, in PACKER it is set according to class assignment. For known members of the target category, $f(x_j) = \gamma$. For members of contrast categories, $f(x_j) = -1 + \gamma$. $\gamma$ is thus a free parameter ($0 \leq \gamma \leq 1$) controlling the trade-off between within-class similarity and between-class dissimilarity: $\gamma = 1$ produces exclusive consideration of same-category members, and $\gamma = 0$ produces exclusive consideration of opposite-category members. When $\gamma = 0.5$, the similarity to contrast categories is effectively subtracted from the similarity to the target category.

>>>>

@@

\section{Description of the non-variant effect of gamma on generation and assignment probabilities
in PACKER}

This document refers to the version of PACKER as described in the manuscript submitted to Cognitive
Psychology (sometime in 2017; henceforth referred to as the manuscript). In this version, PACKER
performs very well in predicting the generation of new category exemplars. In particular, the
tradeoff parameter (henceforth $\gamma$) actually affects the predictions generated in an expected
way. However, when trying to produce predictions of category assignments, varying $\gamma$ does not
affect the predictions in any way. The following section of this document describes why this is
occurring.

Equation 2 in the manuscript specifies that the aggregated similarity $a$ between generation
candidate $y_i$ and a vector of stored exemplars $x$ can be expressed as:

\begin{equation} a(y_i, x) = \sum_j{f(x_j) s(y_i, x_j)}
\label{eq:aggsim}
\end{equation} where $f(x_j) = \gamma$ when $x_j$ is a member of a target category and $f(x_j) =
\gamma - 1$ when $x_j$ is a member of a contrast category.

We can express Equation \ref{eq:aggsim} here a little differently:

\begin{equation} a(y_i,x) = \gamma \sum_k{s(y_i,x_k)} + (\gamma-1) \sum_l{s(y_i,x_l)}
\label{eq:aggsimsplit}
\end{equation} where $k$ iterates over members of the target category and $l$ iterates over members
of the contrast category. To make the algebra a little less tedious we can simplify some of the
representations here. Let $t_i = \sum_k{s(y_i,x_k)}$ and $c_i = \sum_l{s(y_i,x_l)}$, which allows us to
express Equation \ref{eq:aggsimsplit} as:

\begin{equation} a(y_i,x) = \gamma t_i + (\gamma-1) c_i .
\label{eq:aggsimsimp}
\end{equation}

According to the implementation of PACKER as seen in the manuscript, an exponentiated Luce's choice
rule is used to find the probability $p$ of generating candidate $y_i$:

\begin{equation} p(y_i) = \dfrac{\exp \{\theta \cdot a(y_i, x)\}} {\sum_i{\exp \{\theta \cdot
a(y_i,x)\}}} .
\end{equation} 
Thus far, these equations only apply to predictions of category generation. However, predictions of
category assignments require some reconceptualization of these equations, although most of the
equations retain the same structure. Specifically, for Equations \ref{eq:aggsim} to
\ref{eq:aggsimsimp}, $y_i$ now represents the assignment of candidate $y$ to target category $i$.

expanding $a(y_i,x)$ with Equation \ref{eq:aggsimsimp}:
\begin{equation} p(y_i) = \dfrac{\exp \{\theta \cdot \gamma t_i + (\gamma-1) c_i\}} {\sum_i {\exp
      \{\theta \cdot \gamma t_i + (\gamma-1) c_i\}}}
\label{eq:expluceexp}
\end{equation}

Whereas the denominator in Equation \ref{eq:expluceexp} is the summation of aggregated similarities
over all generation candidates in category generation, category assignment predictions require that
the denominator specifies the summation over all category assignments. Specifically, $i$ in the
summation term represents each category, as opposed to each generation candidate.

@@

Where $f(x_j)$ is a function specifying each stored example's degree of contribution toward
generation. Although $f(x_j)$ may be set arbitrarily, in PACKER it is set according to class
assignment. For known members of the target category, $f(x_j) = \gamma$. For members of contrast
categories, $f(x_j) = \gamma - 1$. $\gamma$ is thus a free parameter ($0 \leq \gamma \leq 1$)
controlling the trade-off between within-class similarity and between-class dissimilarity: $\gamma =
1$ produces exclusive consideration of same-category members, and $\gamma = 0$ produces exclusive
consideration of opposite-category members. When $\gamma = 0.5$, the similarity to contrast
categories is effectively subtracted from the similarity to the target category.
